\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-07-25 syntax.tex
Adding references for W-type

Recall in W-type~\cite{martin1982constructive}, a pair of type $x : A
\vdash B(x)$ decides a W-type. To simulate extensible inductive types, we
have to equip our inductive types with multiple constructors, and for
simplicity, each constructor has a fixed form \mintinline{agda}{cstrᵢ :
(x : Aᵢ) → (Bᵢ x → W) → W}.
Thus, we use a `list' of pairs ($\goodWSig{\Gamma}{w^+~A_i~B_i~\tau}{}$) as the signature of one
inductive type. Given an inductive type signature, we can use
\ruleref{WSig-Proj} to extract the corresponding $A_i, B_i$.

>>>>

We base our formalization of the inductive type on W-type~\cite{martin1982constructive}. 
W-type, despite of the simplicity of its formulation, is able to construct a wide range of inductive type in extensional setting~\cite{martin1984intuitionistic,dybjer1997representing,abbott2004representing} and intensional setting (with the help of identity type~\cite{hugunin2021not}).
Recall in W-type, a pair of type $x : A
\vdash B(x)$ decides a W-type. To simulate extensible inductive types, we
have to equip our inductive types with multiple constructors, and for
simplicity, each constructor has a fixed form \mintinline{agda}{cstrᵢ :
(x : Aᵢ) → (Bᵢ x → W) → W}.
Thus, we use a `list' of pairs ($\goodWSig{\Gamma}{w^+~A_i~B_i~\tau}{}$) as the signature of one
inductive type. Given an inductive type signature, we can use
\ruleref{WSig-Proj} to extract the corresponding $A_i, B_i$.
